---
title: "Craps Report"
author: "Jeremy Werner"
date: "Thursday, February 12, 2015"
output: html_document
---

<!-- Here is the R markdown script from one discussion. Please view it for practice and ilustration. (Also, for reference, this text inside these arrows is an HTML comment) --> 

First, let's define some functions to simulate a craps game.

## Define functions

1. This function returns a random di roll
```{r}
roll = function(){
  return(sample(1:6,1))
}
```

2. This function appends a given `val` to the given `input` list.
```{r}
list_append = function(input, val){
  n = length(input)
  input[[n+1]] = val
  return(input)
}
```

3. This function simulates a craps game and returns all of the roll totals and the points that were achieved during one round.
```{r}
game = function(){
  point = 0
  craps = FALSE
  all_rolls = list()
  all_points = list()
  
  while(!craps){
    r1 = roll()
    r2 = roll()
    if(point > 0){
      if((r1+r2) == 7){
        craps = TRUE
      }
      if((r1+r2) == point){
        all_points = list_append(all_points, point)
        point = 0
      }
    }else{
      if((r1+r2) %in% c(4,5,6,8,9,10)){
        point = r1+r2
      }
    }
    all_rolls = list_append(all_rolls, c(r1,r2)) 
  }
  return(list("rolls" = unlist(lapply(all_rolls, sum)), "points" = unique(unlist(all_points))))
}

```


4. This function will simulate one game and return the corresponding winnings for the given `bet` amount if a fire bet is achieved.
```{r}
fire_bet = function(bet){
  win = 0
  game_data = game()
  unique_p = length(game_data$points)
  if(unique_p > 3){
    win = bet * c(25, 250, 1000)[unique_p - 3]
  }
  return(win)
}

```

5. This function will simulate `rounds` number of craps games and return the net winnings for *only* fire bets corresponding to the bet amount `in_bet`.
```{r}
fire_bet_winnings = function(rounds, in_bet){
  win_vector = sapply(1:rounds, function(i, bet2){
    return(fire_bet(bet2))
  }, bet2 = in_bet)
  net_winnings = -1 * rounds * in_bet + sum(win_vector)
  return(net_winnings)
}
```


## Simulations

1. Simulated net winnings for betting $5 on a fire bet for 1000 rounds
```{r}
fire_bet_winnings(1000,5)
```

2. Simulated net winnings for betting $1 on a fire bet for 10000 rounds
```{r}
fire_bet_winnings(10000,1)
```

3. Plot of fire bet winnings for a $5 bet over 1000 rounds

```{r, echo = FALSE}
x = 1:1000
y = sapply(x, function(i){return(fire_bet(5))})
indices = as.numeric(y > 0) + 1
plot(x,y, col = c("black", "red")[indices], pch = c(".","W")[indices], xlab = "Game Number", ylab = "Fire Bet Winnings")
```

4. Total winnings for above simulation
```{r, echo=FALSE}
sum(y)
```

(Misc from discussion) 

#### THIS. IS. MARKDOWN!!!

Here is some math: $\sum\limits_{i=1}^{500} x_i^2\alpha$

